Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-19 journal/article.tex
Training and coaching

\begin{table}[h]
    \centering
    \begin{tabular}{ l l }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Training is necessary to achieve change  &  P3, P6, P14, 16, P30  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investment and resourcing factors that affect
             transformation negatively}
    \label{table:challenges_lackofinvestment}
\end{table}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Training is necessary to achieve change  &
                P3, P6, P11, P14, P16, P30, P37, P46 \\
        Coaching is essential in transformation  &
                P3, P6, P8, P9 P16, P17, P18, P30, P42, P44, P47, P48  \\
        \bottomrule
    \end{tabular}
    \caption{XXXXXXXXXXXXXX}
    \label{table:success_NN}
\end{table}

@@

Agile methods avoid prescribing exact ways of working but rather emphasize a
mindset of adapting to the situation. It is difficult to explain by theory how
such a mindset should be applied, and the agile practices are best learnt by
doing. Coaching teams while they apply the agile methods in practice was seen as
an important factor in change [P3, P16, P17, P30, P47]. A few cases stated even
that coaching was essential for success in transformation [P8, P18]. Also,
without coaching teams can do damage to the agile transformation if techniques
are applied improperly [P9].

There were a number of statements of the benefits of coaching. The coach
position allowed to watch for and correct problems when they arose [P16, P42].
Coaches also helped to draw attention away from focus on tools and towards
understanding the principles of agile [P42, P48].
There were also benefits in using both internal and external coaches.
External coaches were able to have an objective view of the organization [P16,
P44], but internal coaches were more accessible and knew the specifics of the
organization [P3, P6].

\subsubsection{Choosing the agile model}

The choice of agile practices did affect the success of the transformation.
Also how the practices were choosen affected.

% %%%%%%%%%%%%%%%%%%%%%%%%%%
